---
title: "Manipulating Time Series Data in R with xts & zoo"
output: 
  html_notebook:
    toc: yes
---

#Introduction to eXtensible Time Series, using xts and zoo for time series 

xts and zoo are just two of the many different types of objects that exist in R. 

This chapter will introduce the basic objects in xts and zoo and their components, and offers examples of how to construct and examine the data. 

**xts** extends the popular **zoo** package

* xts objects are matrix objects internally.

* xts objects are indexed by a formal time object.

* Most zoo methods work for xts.

### More than a matrix

It is best to think of xts objects as normal R matrices, but with special powers. These powers let you manipulate your data as a function of time, as your data is now self-aware of when it exists in time. Before we can start to exploit these powers, it will be helpful to see how xts objects relate to their base-R relatives.

In this exercise, you will get a feel for xts and how it behaves like a matrix object. The xts object ex_matrix and matrix object core have been pre-loaded for you.

```{r eval=TRUE, echo = FALSE}
library(xts)
```

```{r echo = TRUE, eval=FALSE}
# Load xts
library(xts)

# View the structure of ex_matrix
str(ex_matrix)

# Extract the 3rd observation of the 2nd column of ex_matrix
ex_matrix[3, 2]

# Extract the 3rd observation of the 2nd column of core 
core[3, 2]

```


```{r echo = TRUE, eval=TRUE}

# Create the object data using 5 random numbers
data <- rnorm(5)

# Create dates as a Date class object starting from 2016-01-01
dates <- seq(as.Date("2016-01-01"), length = 5, by = "days")

# Use xts() to create smith
smith <- xts(x = data, order.by = dates)

# Create bday (1899-05-08) using a POSIXct date class object
bday <- as.POSIXct("1899-05-08")

# Create hayek and add a new attribute called born
hayek <- xts(x = data, order.by = dates, born = bday)
print(hayek)
```



### Converting xts objects


```{r echo = TRUE, eval=TRUE}
# Convert austres to an xts object called au
au <- as.xts(austres)

# Then convert your xts object (au) into a matrix am
am <- as.matrix(au)

# Inspect the head of am
print(head(am))

# Convert the original austres into a matrix am2
am2 <- as.matrix(austres)

# Inspect the head of am2
print(head(am2))

```